Actuator line modeling of vertical-axis turbines

### 2016-08-27 reviews/reviewer1-response.md

We have not plotted the LES results, since we only used LES for one tip speed
ratio, and for one turbine---it was mainly employed to assess wake predictions.

>Page 11, Line 42: I'm not quite sure if what you have stated about Smagorinsky
model is correct. It certainly is very easy to implement and gives nice results
in some cases, but we are all aware of its deficiencies. We set a fix Cs value
which means we add numerical dissipation to the whole computatiponal domain, but
this is not really accurate when dealing with cases with strong directional
homogeneity and anisotropy. Why didn't you choose a dynamic Smagorinsky or even
dynamic Lagrangian model? Besides, what is the Cs value you have used?

Firstly, the $C_S$ value used was OpenFOAM's default value of approximately
0.17. This detail has been added to the text.

Secondly, we are not trying to claim that the Smagorinsky model is the most
accurate "standard" model, but that is has been used in many other ALM papers,
and therefore a good baseline for comparison. The wording of the text has been
adjusted to reflect the notion that we are interested in this comparison to
baseline for turbine ALM modeling, and are by no means implying that this SGS
model is the most accurate or appropriate for this case. Certainly testing
additional SGS models will be part of future work, as is mentioned in the
conclusions.

>Page 13, Fig 15: Following my last comment, figure to the right may very well
explain that the Smagorinsly model has been over dissipative thereby hampering
turbulent fluctuations which may have otherwise resulted in higher TKEs.

This is a valid point, and we have added a comment to the text accordingly. It
is important to note, however, that since we don't have near-wall boundary
layers, it may be that turbulence is only generated by larger-scale shear and
vortex breakdown, rather than by boundary layer separation or transition, which
would occur with a body-fitted mesh.

>Page 14, Line 27: Matching mean velocities is usually rather straightforward (in non-presudospectral
codes, sometimes even shutting down the whole SGS modeling wouln'd make a difference as long as no solid walls are involved). But higher order moments such as Reynolds stress tensor components are usually more sensitive. Perhaps you can go more in depth with that part -- possibly compare your
results with other experiments or CFD simulations. Besides, please try and overcome the relatively large discrepancies seen in figures 6 (high TSR), 9, 11.

### 2016-08-27 paper.tex
Address comment about over-dissipative nature of Smagorinsky model

Mean velocity profiles at the turbine center plane, plotted in
Figure~\ref{fig:RVAT-ALM-LES-profiles}, were predicted more accurately using LES
versus RANS, and rival those of the 3-D blade-resolved models. However,
turbulence kinetic energy profiles did not match as closely with experiments.
Though the qualitative shape was resolved better than that by the RANS ALM
simulation, notably the asymmetric peaks around $y/R = \pm 1$, the turbulence
generated in the large eddy simulation was approximately an order of magnitude
too low. Once again this was probably a result of the subgrid-scale modeling and
its effect on the stability of vortex structures.

>>>>

Mean velocity profiles at the turbine center plane, plotted in
Figure~\ref{fig:RVAT-ALM-LES-profiles}, were predicted more accurately using LES
versus RANS, and rival those of the 3-D blade-resolved models. However,
turbulence kinetic energy profiles did not match as closely with experiments.
Though the qualitative shape was resolved better than that by the RANS ALM
simulation, notably the asymmetric peaks around $y/R = \pm 1$, the turbulence
generated in the large eddy simulation was approximately an order of magnitude
too low. Once again this was likely a result of the subgrid-scale modeling and
its effect on the stability of vortex structures, or its over-dissipative nature
removing energy from the flow before it is advected to the plane of interest.
